Sentences for use in Experiment 2

### 2011-02-25 aux/material_exp2/sentences.tex
material 2nd experiment updated after meeting

\begin{itemize}
\item target sentences have a scalar item embedded under a quantifier
  \begin{itemize}
  \item embedding quantifiers:
    \begin{enumerate}
    \item definite article \attrib{(for baseline)}
    \item ``einige'' \attrib{(upward monotonic)}
    \item ``alle'' \attrib{(upward monotonic)}
    \item ``genau ein'' \attrib{(non-monotonic)}
    \end{enumerate}
  \item two scalar items in embedded position:
    \begin{enumerate}
    \item ``einige''
    \item ``oder''
    \end{enumerate}
  \end{itemize}
  \begin{exe}
  \ex \label{bsp:target1} Der \dots ist mit einigen seiner \dots
    verbunden. \attrib{($\iota\exists$)}
  \ex Einige der \dots sind  mit einigen ihrer \dots
    verbunden. \attrib{($\exists\exists$)}
  \ex Alle der \dots sind  mit einigen ihrer \dots verbunden. \attrib{($\forall\exists$)}
  \ex Genau einer der \dots ist  mit einigen seiner \dots verbunden. \attrib{($!\exists\exists$)}
  \ex Der \dots ist mit seinem \dots oder \dots verbunden. \attrib{($\iota\vee$)}
  \ex Einige der \dots sind  mit ihrem \dots oder \dots verbunden. \attrib{($\exists\vee$)}
  \ex Alle der \dots sind  mit ihrem \dots oder \dots verbunden. \attrib{($\forall\vee$)}
  \ex Genau einer der \dots ist  mit seinem \dots oder \dots verbunden. \attrib{($!\exists\vee$)}
  \end{exe}
\item each target sentence should occur in four (or three?) versions,
  e.g.:
  \begin{exe}
  \exr{bsp:target1} Der \dots ist mit einigen seiner \dots
    verbunden. \attrib{($\iota\exists$)}
    \begin{xlist}
    \ex Der \dots ist mit einigen seiner \dots
      verbunden. \attrib{(flat)}
    \ex Der \dots ist mit \emph{einigen} seiner \dots
      verbunden. \attrib{(stress)}
    \ex Der \dots ist nur mit einigen seiner \dots
      verbunden. \attrib{(only, flat)}
    \ex Der \dots ist nur mit \emph{einigen} seiner \dots
      verbunden. \attrib{(only, stress)}
    \end{xlist}
  \end{exe}

\end{itemize}

>>>>

\begin{itemize}
\item target sentences have a scalar item embedded under a quantifier
  \begin{itemize}
  \item embedding quantifiers:
    \begin{enumerate}
    \item ``alle'' \attrib{(upward monotonic)}
    \item ``genau ein'' \attrib{(non-monotonic)}
    \end{enumerate}
  \item two scalar items in embedded position:
    \begin{enumerate}
    \item ``einige''
    \item ``oder''
    \end{enumerate}
  \end{itemize}
  \begin{exe}
  \ex \label{bsp:target1} Alle der \dots sind  mit einigen ihrer \dots
    verbunden. \attrib{($\forall\exists$)}
  \ex Genau einer der \dots ist  mit einigen seiner \dots verbunden. \attrib{($!\exists\exists$)}
  \ex Alle der \dots sind  mit ihrem \dots oder \dots verbunden. \attrib{($\forall\vee$)}
  \ex Genau einer der \dots ist  mit seinem \dots oder \dots verbunden. \attrib{($!\exists\vee$)}
  \end{exe}
\item each target sentence should occur in three versions, e.g.:
  \begin{exe}
    \exr{bsp:target1} Alle der \dots sind mit einigen ihrer \dots
    verbunden. \attrib{($\forall\exists$)}
    \begin{xlist}
    \ex  Alle der \dots sind mit einigen ihrer \dots
      verbunden. \attrib{(flat)}
    \ex Alle der \dots sind mit \emph{einigen} ihrer \dots
      verbunden. \attrib{(stress)}
    \ex Alle der \dots sind nur mit \emph{einigen} ihrer \dots
      verbunden. \attrib{(only + stress)}
    \end{xlist}
  \end{exe}
\item we test for 3 possible readings of each target sentence
\end{itemize}
